Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2017-03-27 paper/presentation/DASFAA_presentation.tex
some fix

%------------------------------
%page 12
\begin{frame}
\frametitle{Experimental Results}
Evaluation on Categroy-Level Topics in Knowledge Base. On \textit{Aviation} topic, semantic coherence is much better than LightLDA (same as LDA) in terms of NPMI[Röder, WSDM 2015]\footnote{\url{https://github.com/AKSW/Palmetto}}.

>>>>

%------------------------------
%page 12
\begin{frame}
\frametitle{Experimental Results}
Evaluation on Categroy-Level Topics in Knowledge Base. On \textit{Aviation} topic, semantic coherence is much better than LightLDA (same as LDA) in terms of NPMI[Roder, WSDM 2015]\footnote{\url{https://github.com/AKSW/Palmetto}}.
